What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-10-22 manuscript.Rmd

A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired]. Historically, this option has not been available for eye-tracking. This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking [e.g., @snedeker2003using]. Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic. In recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation]. However, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].

>>>>

A robust solution to all these problems is online experiments, particularly with volunteer citizen scientists as participants [@li2024developmental; @hartshorne2019thousand; @reinecke2015labinthewild; @gosling2010wired]. Historically, this option has not been available for eye-tracking. This began to shift with the widespread incorporation of cameras into computers; researchers have long used frame-by-frame analysis of video for low-resolution eyetracking [@snedeker2003using]. Unfortunately, this can be extremely time-intensive, making large-sample studies unrealistic. In recent years, image analysis has improved to the point where this work can be automated with reasonable accuracy [@papoutsaki2016webgazer; @zheng2018rapid; @burton2014comparison; @skovsgaard2011evaluation]. However, webcam-based eyetracking only started to be used regularly in research with the advent of `Webgazer.js` [@papoutsaki2016webgazer], a webcam-based Javascript plug-in that works in the browser and which can be integrated with any Javascript web interface, including `jsPsych` [@deleeuwJsPsychJavaScriptLibrary2015], `Gorilla` [@anwyl2020gorilla], or `lab.js` [@henninger2021lab].
